LSOA domestic Electricty and Gas maps

### 2021-09-02 LSOA domestic Elec and Gas.Rmd

# check IMD decile is higher with higher deprivation
library(data.table)
dt <- as.data.table(Solent)
dt[, .(nLSOAs = .N,
       meanIMDScore = mean(IMDScore)),
   keyby = .(IMD_Decile)]

@@

NB: IMD Decile 10 has _LOWER_ IMD score!

>>>>

@@

NB: IMD Decile 10 has _LOWER_ mean IMD score! Which is what it says in the Excel workbok...
